% 25 Mar 2014 : GWA : Goal is 1.5 pages including scenarios and a taxonomy of
% different types of mocking.

\begin{table*}[t]

\input{./figures/surveytable.tex}

\caption{\textbf{Detailed mocking survey results.} All values are percentages
of the 91 respondents. Levels of knowledge we considered to be unreasonable
are marked in bold in the accuracy row.}

\label{table-surveyresults}

\end{table*}

\section{Scenarios}
\label{sec-scenarios}

To make our earlier description of app mocking more concrete, consider these
four scenarios:

\begin{itemize}

\item Bob wants to appear more active. On Monday he takes a walk to get some
exercise. The next day, he doesn't take a real walk, but while he is sitting
at his desk his smartphone mocks another walk.

\item Alice wants to appear more healthy, but on Monday she visits a fast
food restaurant where she enjoys an unwholesome meal. As she eats, however, her
smartphone mocks a visit to a nearby organic salad delicatessen.

\item Teenager Jerry's parents use a smartphone app to monitor his late-night
  ventures and to ensure that he returns home by an imposed curfew. One
  night Jerry remains out on the town later-than-allowed with his friends,
  but his phone has already mocked him dutifully returning home on time.

\item Carol's employer uses her phone to monitor her attendance. During the
workday, she surreptitiously slips out for a latte with a friend.  Meanwhile,
her phone records her apparent continued presence at her desk.

\end{itemize}

These examples highlight the difference between \textit{privacy} and
\textit{mocking}. None of our characters' objectives can be accomplished
through privacy, since in each case achieving the objective requires using
data to manipulate an app. Of course, Jerry could remove the app that his
parents installed, as could Carol, but his parents and her employer would
likely notice. In the cases of Alice and Bob, we can assume that they have
been asked or incentivized to install these health-monitoring apps but may
not feel fully-comfortable with their operation. Similarly, however, removing
or disabling the apps may not be an attractive option. We include a more
in-depth discussion of the practical and ethical implications of mocking in
Section~\ref{sec-ethics} after establishing the feasibility and desirability
of this approach.
